Concurrent Programming with Harmony

### 2020-07-28 book/paper.tex
Working on Section 8

\autoref{fig:tas} goes on how to implement mutual exclusion for
a set of \texttt{N} processes.
The approach is called \emph{spinlock},
\index{spinlock}%
because each process is ``spinning'' until
it can acquire the lock.
The program uses $\mathtt{N}+1$ variables.
Variable \textit{shared} is initialized to \texttt{False} while
\textit{private}[$i$] for each process $i$ is initialized to \texttt{True}.
An important invariant, $\mathcal{I}_1$, of the program is that at any time at most
one of these variables is \texttt{False}.
Another invariant, $\mathcal{I}_2(i)$, is that if process $i$ is in the critical section,
then \textit{private}[$i$] == \texttt{False}.
Between the two (i.e., $\mathcal{I}_1 \land \forall i: \mathcal{I}_2(i)$),
it is clear that only one process can be in the
critical section at the same time.

>>>>

\autoref{fig:tas} goes on to implement mutual exclusion for
a set of \texttt{N} processes.
The approach is called \emph{spinlock},
\index{spinlock}%
because each process is ``spinning'' (executing a tight loop) until
it can acquire the lock.
The program uses $\mathtt{N}+1$ variables.
Variable \textit{shared} is initialized to \texttt{False} while
\textit{private}[$i$] for each process $i$ is initialized to \texttt{True}.
An important invariant, $\mathcal{I}_1$, of the program is that at any time at most
one of these variables is \texttt{False}.
Another invariant, $\mathcal{I}_2(i)$, is that if process $i$ is in the critical section,
then \textit{private}[$i$] == \texttt{False}.
Between the two (i.e., $\mathcal{I}_1 \land \forall i: \mathcal{I}_2(i)$),
it is clear that only one process can be in the
critical section at the same time.
